Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-04-28 WSSSPE4_report/wg_codemeta.tex
removing more author name notes

\note{Alice to write this}

This group, which included people who had previously been working on the CodeMeta project\footnote{\url{http://codemeta.github.io/}}, formed to address the proposed project,
 ``Define a standard for metadata to be used in current repos including authors, dependencies, ... repo url.''

>>>>

%\note{Alice to write this}

This group, which included people who had previously been working on the CodeMeta project\footnote{\url{http://codemeta.github.io/}}, formed to address the proposed project,
 ``Define a standard for metadata to be used in current repos including authors, dependencies, \dots{}, repo URL.''
